A Survey of Wearable Device Risk Perceptions

### 2015-01-06 wearables_survey.tex
Started adding regression model

\subsubsection{Regression Model} 
{\color{red} SERGE TODO: fill in this section.}

>>>>

\subsubsection{Regression Model} 
In order to examine the relative effect of each factor on participants' VURs, we constructed a statistical model to predict whether a participant would be ``very upset'' with a given scenario based on the data type, device, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes). We performed a binary logistic regression using generalized estimating equations, which accounts for our repeated measures experimental design (i.e., each participant contributed multiple data points).
